---
title: "Exploration and Models"
author: Elizabeth Khan, Estrella Ndrianasy, Chandni Shah, Michelle Shen, Catherine
  Tsai
date: "November 8, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(magrittr)
library(ggplot2)
library(sandwich)
library(lmtest)
library(stargazer)
library(stringr)
library(tidyverse)
library(gtsummary)
library(vtable)


theme_set(theme_minimal())
options(tinytex.verbose = TRUE)
options(warn=-1)
```

## 
Import data and remove invalid age; create column to indicate wheter or not subject has a college degree


```{r survey}
d <- fread("survey_cleaned_with_states.csv")
head(d)
d <- d[Age!='Other']

degrees = c("Bachelors degree","Associates degree","Masters degree")

d<- d[,college_degree:= ifelse(Education %in% degrees, 1,0)]
length(d$college_degree)
```

## Randomness Check

In this section, we verify if the block randomization was successful; there should be no increase in predicting whether or not someone is in the treatment or control group based on their blocks.

```{r}
null_model <- lm(assigned~1,data=d)
full_model <- lm(assigned ~ 1 + as.factor(Age)+as.factor(Gender), data=d)
f_test <- anova(full_model, null_model, test ='F')
f_test
```
Based on the F-test results there is no evidence to suggest the adding in the block covariates increased the accuracy of predicting whether or not the subject received the treatment.

## Plots and Tables

Summary of subject assignment and demographics

```{r plots, echo=FALSE}
d %>%
  select(Gender, assignment, Age) %>%
  tbl_summary(by = Gender) %>%
  add_overall()
```
```{r}
d %>%
  select(Gender, Education, assignment) %>%
  tbl_summary(by = assignment) %>%
  add_overall()
```
```{r}
cols <- c("instr_enthusiasm","instr_professional", "instr_subject","instr_material","instr_rating","avg_rating","assignment")

st(d[,..cols], group = 'assignment',
   summ = list(
     c('notNA(x)','mean(x)'),
     c('notNA(x)','mean(x)')
   ),
   summ.names = list(
     c('N','Mean'),
     c('Count','Percent')
   ), out='htmlreturn')


st(d[,..cols], group = 'assignment', group.test=TRUE, out='kable')

```
```{r}

d$quiz_grade <- as.factor(d$quiz_avg*100)
ggplot(d, aes(x=quiz_grade))+
geom_bar(aes(y = (..count..)),fill="lightblue")+
labs(title="Distribution of Retention Quiz Scores",
        x ="Retention Quiz Score", y = "Count")

```

```{r}
ggplot(d, aes(x=assignment, y=avg_rating, fill=assignment))+
  geom_boxplot()+
  labs(title="Bar Chart of Treatment Assignment versus Average Instructor Rating",
        x ="Treatment Assignment", y = "Average Instructor Rating")
```
```{r}
ggplot(d, aes(x=video_watched, y=avg_rating, fill=assignment))+
  geom_boxplot()+
  labs(title="Bar Chart of Video Watched versus Average Instructor Rating",
        x ="Video Watched", y = "Average Instructor Rating")+theme(axis.text.x = element_text(angle = -30))
```
```{r}
ggplot(d, aes(x=video_watched, y=instr_enthusiasm, fill=assignment))+
  geom_boxplot()+
  labs(title="Bar Chart of Video Watched versus Average Instructor Enthusiasm",
        x ="Video Watched", y = "Instructor Enthusiasm Rating")+theme(axis.text.x = element_text(angle = -30))
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
model_1 <- lm(avg_rating ~ as.factor(Age) + as.factor(Gender)+assignment, data=d)
model_2 <- lm(instr_rating ~ as.factor(Age) + as.factor(Gender)+ assignment, data=d)
model_3 <- lm(instr_subject ~ as.factor(Age) + as.factor(Gender)+assignment, data=d)
model_4 <- lm(instr_material ~ as.factor(Age) + as.factor(Gender)+assignment, data=d)
model_5 <- lm(instr_enthusiasm ~ as.factor(Age) + as.factor(Gender)+assignment , data=d)
model_6 <- lm(instr_enthusiasm ~ as.factor(Age) + as.factor(Gender)+assignment +as.factor(Gender)*assignment, data=d)
model_7 <- lm(avg_rating ~ as.factor(Age) + as.factor(Gender)+assignment +as.factor(Gender)*assignment, data=d)
model_8 <- lm(instr_rating ~ as.factor(Age) + as.factor(Gender)+assignment +as.factor(Gender)*assignment, data=d)
```
```{r}
#models with blocking across instructor ratings
stargazer(model_1, model_2, model_3,model_4, model_5, type = 'text')

#interaction term models
stargazer( model_6, model_7, model_8, type = 'text')
```
```{r baseline_models}
# does having a college degree have an effect
mod <- lm(instr_rating ~  as.factor(Age) + as.factor(Gender)+ as.factor(college_degree) + assignment, data=d)
mod_2 <- lm(instr_subject ~  as.factor(Age) + as.factor(Gender)+ as.factor(college_degree) + assignment, data=d)
mod_3 <- lm(instr_material ~  as.factor(Age) + as.factor(Gender)+ as.factor(college_degree) + assignment, data=d)
mod_4 <- lm(instr_enthusiasm ~  as.factor(Age) + as.factor(Gender)+ as.factor(college_degree) + assignment, data=d)
mod_5 <- lm(avg_rating ~  as.factor(Age) + as.factor(Gender)+ as.factor(college_degree) + assignment, data=d)

stargazer(mod,mod_2, mod_3, mod_4,mod_5, type='text')

```
```{r avg_score}
quiz_mod <- lm(quiz_avg ~  as.factor(Age) + as.factor(Gender) + assignment, data=d)
quiz_mod_2 <- lm(quiz_avg ~  as.factor(Age) + as.factor(Gender) + as.factor(Education)+ assignment, data=d)
stargazer(quiz_mod, quiz_mod_2, type='text')
```

```{r}
# Does education level have an effect
mod_2 <- lm(instr_rating ~  as.factor(Age) + as.factor(Gender)+ as.factor(Education) + assignment, data=d)
mod_2_2 <- lm(instr_subject ~  as.factor(Age) + as.factor(Gender)+ as.factor(Education) + assignment, data=d)
mod_2_3 <- lm(instr_material ~  as.factor(Age) + as.factor(Gender)+ as.factor(Education) + assignment, data=d)
mod_2_4 <- lm(instr_enthusiasm ~  as.factor(Age) + as.factor(Gender)+ as.factor(Education) + assignment, data=d)
mod_2_5 <- lm(avg_rating ~  as.factor(Age) + as.factor(Gender)+ as.factor(Education) + assignment, data=d)

stargazer(mod_2,mod_2_2, mod_2_3, mod_2_4,mod_2_5, type='text')
```